Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-03-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@

>>>>

There are only a few involvement patterns for which the model's prediction does not match the prevalence of the data with perfect accuracy. But in these instances, e.g. the case where \gls{lnl} III is metastatic while \gls{lnl} IV is healthy in an early T-category patient (\cref{fig:bg_prevalences}, third row, green line and histogram), the model slightly overestimates the prevalence. An overestimation by a few percent however, does not pose a risk to the model's clinical applicability, since in the context of volume-deescalation, this can be considered cautious.

It is interesting to note that not all involvement patterns become more prevalent with advanced T-category. For example, a healthy \gls{lnl} III is observed slightly less often together with a metastatic level II in advanced, compared to early T-category. This is because in the latter instance, it is more likely the disease has already spread to \gls{lnl} III. Our model captures this accurately and precisely.

@@

\begin{figure}
    \script{comp_IIandV_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_IIandV_prevs.png}
        \caption{TODO: Write Caption.}
        \label{fig:IIandV_prevs}
    \end{centering}
\end{figure}
